\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-15 chapters/3_algorithm.tex
Partial algorithm description; add new figs/tables

    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State Initialize contracted graph $\mathcal{G}'(V',E')$ from $\mathcal{G}$
      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      \State Sort edges in priority queue (PQ) in desc. order of $|W_e|$ 
      \State
      \While{PQ is \textbf{not} empty}
        \State Pop edge $e_{uv}\in E'$ with highest abs. priority $|\tilde{w}|$
        \State
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust.png}
\caption{\small 
Example of agglomerative clustering on signed graph with sum update rule and without Cannot-Link-Constraints. The final clustering is given by one single cluster.
\label{fig:example_non_unique_weights_1}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/aggl_clust_with_nonlink.png}
\caption{\small 
Example of agglomerative clustering on signed graph with sum update rule and using Cannot-Link-Constraints. Edges flagged with \texttt{canBeMerged} = \texttt{False} are highlighted in pink. 
\label{fig:example_non_unique_weights_2}}
\end{figure}

\begin{table*}[h]
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Use Cannot-Link-Constraints:}} \\

\section{Unified Graph Agglomerative Clustering \\Algorithm}
In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms. It can be used to describe both unsigned clustering algorithms ingesting positive similarities between clusters and signed clustering algorithms using attractive and repulsive cues.\\
First, we define the graph notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}

@@

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph!
\item Introduce concept of cannot-link-constraints
\item From wiki: \emph{Both a must-link and a cannot-link constraint define a relationship between two data instances. A must-link constraint is used to specify that the two instances in the must-link relation should be associated with the same cluster. A cannot-link constraint is used to specify that the two instances in the cannot-link relation should not be associated with the same cluster. These sets of constraints acts as a guide for which a constrained clustering algorithm will attempt to find clusters in a data set which satisfy the specified must-link and cannot-link constraints. Some constrained clustering algorithms will abort if no such clustering exists which satisfies the specified constraints. Others will try to minimize the amount of constraint violation should it be impossible to find a clustering which satisfies the constraints.}

\end{itemize}
\subsection{The algorithm}
\begin{itemize}
\item First give intuitive idea of agglomerative clustering
\item enforce the fact that the cannot-link relations are introduced \textbf{dynamically}

@@

At each iteration, one edge is popped from PQ and it is processed only if it belongs to the contracted graph $\mathcal{G}'$. The algorithm terminates when all edges have been processed. and it has two variants: one adding cannot link constraints and one not using them.
\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
% \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)

@@

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item Linkage criteria in the table:
\begin{itemize}
\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix, also showing that adding or not CLC does not change anything]
\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
\item Greedy Fixation \cite{levinkov2017comparative}, 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
\end{itemize}
\item comment about the fact that sum is not an ultra-metric (say better)
\item In this article we analyze only the simplest (and cheapest) types of update rules, but... Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul)

@@

>>>>

    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State Initialize contracted graph $\mathcal{G}'$ from $\mathcal{G}$
      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      \State Sort edges in priority queue (PQ) in desc. order of $|W_e|$ 
      \State
      \While{PQ is \textbf{not} empty}
        \State Pop edge $e_{uv}$ in $\mathcal{G}'$ with highest priority $|\tilde{w}|$
        \State
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}

@@

\section{Unified Graph Agglomerative Clustering}
In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms. It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
First, we define the graph notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}

@@

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
\item Define multicut and associated energy
\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically...)
\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

\subsection{The algorithm}
\begin{itemize}
  \item We now present our first contribution: a unified algorithm for agglomerative graph clustering that can describe in a simple general form many graph partitioning algorithms previously introduced in the literature \UPDATE{and highlights the existence of totally new algorithms}.
\item We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
\item The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters. The algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \ref{fig:general_idea}b and \ref{fig:general_idea}c).

\item A second variant of the proposed algorithm also introduces cannot-link constraints between clusters during the agglomeration and stops when all the remaining clusters have been previously constrained.

\item During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed.

 \item An efficient way of doing this is presented in Algorithm \ref{main_alg}, which proceeds as follows. \UPDATE{TO BE CONTINUED}
\item The so called contracted graph is initialized from the original graph $\mathcal{G}$ and will represent the clustering $\Pi$ at each iteration of the

@@

At each iteration, one edge is popped from PQ and it is processed only if it belongs to the contracted graph $\mathcal{G}'$. The algorithm terminates when all edges have been processed. and it has two variants: one adding cannot link constraints and one not using them.
\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
% \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
\item Mention precise version in the Appendix
\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)

\item In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 representing strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig. \ref{fig:general_idea}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters}.

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
\caption{\small 
Example of agglomerative clustering on signed graph with and without cannot-link constraints. The final clustering is given by one single cluster.
\label{fig:example_cannot_link_constraints}}
\end{figure}

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item In this section we will list \UPDATE{ALL} (...) algorithms that can be described using the generalized algorithm we presented and define some new ones
\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them
\item First unsigned graphs: the merging tree defined by the algorithm (\textbf{define merge tree somewhere..?}) is equivalent to the hierarchical dendrogram (but careful with the sum...) that we have in HC
\item Then mention CLC and who started using them recently for this type of problem: fixed, then greedyFixation introduced exactly this algorithm as a greedy approx of MC, together with Greedy Additive Edge Contraction
\item MWS: proposes an efficient implementation of this update rule (briefly mention the idea). In the Supplementary material we show that the algorithm they present can be seen as a special case of Unified Graph Agglomerative Clustering with absolute maximum update rule and that adding or not CLC does not change anything
\item Then new versions of avg/complete and single linkage clustering 
\item In this article we analyze only the simplest (and cheapest) types of update rules, but... Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul), size rule by Thorsten
\item comment about the fact that sum is not an ultra-metric (say better)
\end{itemize}

@@

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link-Constraints:}} \\

### 2019-03-15 chapters/5_experiments_cityscapes.tex
Partial algorithm description; add new figs/tables

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\

@@

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
% sum & false & \textbf{-150873} & 99 (??) \\
% sum & true & -150873 & 249 \\
% MutexWatershed & false & -150854 & 100 \\
% mean & false & -150850 & 105 \\
% mean & true & -150848 & 244 \\
% max & true & -149441 & 459 \\
% min & true & -147663 & 186 \\
% min & false & -147663 & 82 \\
% max & false & -103614 & \textbf{16} \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Compare update-rules on fruit-fly large graph}
%     \label{tab:linkage-criteria}
% \end{table*}

>>>>

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c | c}
        Update rule & \makecell{Bias factor $\beta$} & AP & AP 50\%\\ \midrule\midrule
MEAN & thresh035  & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN & thresh035 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
% MEAN & thresh030 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
ORIGINAL \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% MEAN & thresh040 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
MEANconstr & thresh025  & {\color{Orange} 0.3390 } & {\color{ForestGreen} 0.5481 } \\
% MEANconstr & thresh030 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
% MEAN & thresh045 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
% MEAN & thresh050 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
SingleLinkagePlusCLC & thresh050  & {\color{Orange} 0.3252 } & {\color{ForestGreen} 0.5304 } \\
MutexWatershed & thresh045  & {\color{Orange} 0.3214 } & {\color{ForestGreen} 0.5306 } \\
greedyFixation & thresh055  & {\color{Orange} 0.3188 } & {\color{Orange} 0.5271 } \\
% greedyFixation & thresh050 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
% MEANconstr & thresh020 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
% MutexWatershed & thresh050 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
% MEANconstr & thresh035 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% greedyFixation & thresh060 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
GAEC & thresh055  & {\color{Orange} 0.3127 } & {\color{Orange} 0.5114 } \\
% GAEC & thresh050 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
% SingleLinkagePlusCLC & thresh045 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
% GAEC & thresh060 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
% greedyFixation & thresh065 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
% greedyFixation & thresh045 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
% GAEC & thresh065 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
% GAEC & thresh045 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
% MEANconstr & thresh035 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
% MEANconstr & thresh040 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
% GAEC & thresh070 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
% SingleLinkagePlusCLC & thresh055 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
% greedyFixation & thresh070 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
% GAEC & thresh075 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
% greedyFixation & thresh075 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
% SingleLinkagePlusCLC & thresh060 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
% GAEC & thresh035 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% greedyFixation & thresh035 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
% MutexWatershed & thresh040 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
% MEANconstr & thresh050 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
% SingleLinkagePlusCLC & thresh040 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
% SingleLinkagePlusCLC & thresh065 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
% greedyFixation & thresh035 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
SingleLinkage & thresh085 & {\color{Red} 0.2433 } & {\color{Red} 0.4436 } \\
% GAEC & thresh035 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
% SingleLinkage & thresh080 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
% SingleLinkagePlusCLC & thresh070 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
% SingleLinkage & thresh075 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
% MutexWatershed & thresh035 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
% SingleLinkage & thresh070 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
% SingleLinkagePlusCLC & thresh035 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
% SingleLinkage & thresh065 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
% SingleLinkage & thresh060 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
% SingleLinkagePlusCLC & thresh075 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
% SingleLinkage & thresh055 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
% SingleLinkage & thresh050 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
% SingleLinkage & thresh035 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
CompleteLinkagePlusCLC & thresh035  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
CompleteLinkage & thresh035  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

@@

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c| c | c}
%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
%     \label{tab:linkage-criteria}
% \end{table*}

### 2019-03-15 chapters/supplementary.tex
Partial algorithm description; add new figs/tables

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\PassOptionsToPackage{noend}{algpseudocode}% comment out if want end's to show
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

% \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\vrule height .75\baselineskip depth .25\baselineskip}}%

% \newcount\ALG@printindent@tempcnta
% \def\ALG@printindent{%
%     \ifnum \theALG@nested>0% is there anything to print
%         \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
%             % do nothing
%             \addvspace{-3pt}% FUDGE for cases where no text is shown, to make the rules line up
%         \else
%             \unskip
%             % draw a rule for each indent level
%             \ALG@printindent@tempcnta=1
%             \loop
%                 \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
%                 \advance \ALG@printindent@tempcnta 1
%             \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
%             \repeat
%         \fi
%     \fi
%     }%
\usepackage{etoolbox}
% the following line injects our new indent handling code in place of the default spacing
% \patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
% \makeatother
% end vertical rule patch for algorithmicx

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\RED}[1]{#1}

\newcommand\TODO[1]{{\color{red}{TODO: #1}}}
\newcommand\UPDATE[1]{{\color{blue}{#1}}}
\newcommand\SOURCE[1]{{\color{green}{(from: #1)}}}
% \newcommand\CHANGED[2]{{{\color{blue}{#1}}\color{green}{#2}}}

\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for ICCV Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

\input{chapters/abstract.tex}

\input{chapters/intro.tex}

\input{chapters/rel_work.tex}

@@

% \section{Algorithm}
\section{Agglomerative Clustering}
\begin{itemize}
\item Define graph formalism and clustering $\Pi$
\item Description and pseudo-code
\item Linkage criteria in the table:
\begin{itemize}
\item Mutex Watershed \cite{wolf2018mutex}, [proof of equivalence included in Appendix]
\item Greedy Additive Edge Contraction \cite{levinkov2017comparative}, 
\item Greedy Fixation \cite{levinkov2017comparative}, 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) linkage criteria
\end{itemize}
\item Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum

\item Comment about must-not-link relations: they give high priority to the most confident repulsive edges 
\item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
\item comment about complexity (depends on the linkage criteria) and how dense is the graph (check PQ update)
\end{itemize}

\section{Experiments}
\begin{itemize}
\item define pixel grid graph and long range connections
\item probability of long-range connections
\end{itemize}
\subsection{Qualitative comparison}
\begin{itemize}
\item find good way to represent agglomeration order
\item can we display the must-not-link edges...?
\end{itemize}
\subsection{Noise experiments}

\subsection{Comparison on CREMI and cityscapes}

\section{Conclusions}

{\small
\bibliographystyle{ieee}
\bibliography{agglo_clust}
}

\section{Supplementary Material}
\begin{itemize}
\item Equivalence Mutex Watershed and Greedy Edge Contraction
\end{itemize}

\end{document}

>>>>

% !TEX root = ../agglo_clust_review.tex

\section{Supplementary Material}
\begin{itemize}
\item Equivalence Mutex Watershed and Greedy Edge Contraction
\item Complexity: plain agglo., addition of the cannot-link constraints and then comment about efficient implementation of MWS and of single-linkage (what about single linkage+CLC...?)
\end{itemize}

@@
